\documentclass[twoside,openright,titlepage,numbers=noenddot,headinclude,%
               footinclude=true,cleardoublepage=empty,abstractoff,BCOR=5mm,%
               paper=a4,fontsize=12pt,ngerman,american]{scrreprt} %eulermath

% Solve too many packages
\usepackage{etex}
\reserveinserts{28}

% Custom config ===============================================================

% Classic thesis
\usepackage{amssymb}
\input{classicthesis-config}

% Theorems and definitions
\usepackage{amsthm}
\newtheorem{theorem}{Theorem}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{definition}{Definition}

\newtheorem{algorithm}{Algorithm}
\usepackage{algpseudocode}

% Counters
\renewcommand{\labelenumi}{{\color{halfgray}(\alph{enumi})}}
\renewcommand{\labelenumii}{\color{halfgray}{\roman{enumii}.}}
\renewcommand{\labelitemi}{{\color{halfgray}-}}%\raisebox{0.3ex}{\tiny$\blacksquare$}}}

\numberwithin{theorem}{chapter}
\numberwithin{definition}{chapter}
\numberwithin{algorithm}{chapter}
\numberwithin{figure}{chapter}
\numberwithin{table}{chapter}

% Maths
\DeclareMathOperator*{\argmin}{arg\,min}
\DeclareMathOperator*{\argmax}{arg\,max}
\newcommand{\partialb}[2]{\frac{\partial^2 J(\theta)}{\partial\theta_{#1}\partial\theta_{#2}}}

\numberwithin{equation}{chapter}
\allowdisplaybreaks

% Shaded boxes
\usepackage{framed}
\newenvironment{remark}[1]{%
  \definecolor{shadecolor}{gray}{0.9}%
  \begin{shaded}{\color{Maroon}\noindent\textsc{#1}}\\%
}{%
  \end{shaded}%
}

% Code snippets
\usepackage{minted}
\definecolor{rulecolor}{rgb}{0.80,0.80,0.80}
\definecolor{bgcolor}{rgb}{1.0,1.0,1.0}
\newminted{python}{bgcolor=bgcolor}

% Todo
\newcommand{\todo}[1]{\textcolor{red}{[TODO] #1}}

% PS pictures
\usepackage{pstricks,auto-pst-pdf}
\usepackage{epstopdf}

% Landscape tables
% \usepackage{rotating}

% Checkmarks
\usepackage{pifont}% http://ctan.org/pkg/pifont
\newcommand{\cmark}{\ding{51}}%
\newcommand{\xmark}{\ding{55}}%

% Wide tables
% \usepackage{ltablex}

% others
\usepackage{multirow}

\graphicspath{{figures/}}
\DeclareGraphicsExtensions{.pdf,.jpg,.png, .eps}

\usepackage{setspace} 
\setstretch{1.4} 

\usepackage[super]{nth}

% TIKZ flowcharts
\usepackage{tikz}
\usetikzlibrary{shapes.geometric, arrows}

% Fix Hyphenation problems.
\sloppy

% -----------------------------------------------------------------------------

\begin{document}
\frenchspacing
\raggedbottom
\selectlanguage{american}
\pagenumbering{roman}
\pagestyle{plain}


% Front pages =================================================================
\include{frontback/titlepage}
\cleardoublepage\include{frontback/jury}
\cleardoublepage\include{frontback/abstract}
\cleardoublepage\include{frontback/dedication}
\cleardoublepage\include{frontback/acknowledgments}
\pagestyle{scrheadings}
\cleardoublepage\include{frontback/toc}


% Content =====================================================================
\pagenumbering{arabic}

\include{chapters/chapter01}\cleardoublepage
\include{chapters/chapter02}\cleardoublepage

\ctparttext{
Several real-world classification problems are example-dependent cost-sensitive.
For example in credit card fraud detection, failing to detect a fraudulent transaction may have 
an economical impact from a few to thousands of Euros, depending on the particular transaction 
and card holder. In in credit scoring, accepting loans from bad customers does not have the same 
economical loss, since customers have different credit lines, therefore, different profit
Similarly, churn modeling, a model is used for predicting which customers are more likely to 
abandon a service provider. In this context, failing to identify a profitable or unprofitable 
churner has a significant different economic result. Lastly, in direct marketing, wrongly predicting 
that a customer  will not accept an offer when in fact he will, may have different financial impact, 
as not all customers generate the same profit.
}
\part{Real-world applications}\label{part:1}

	\include{chapters/chapter03}\cleardoublepage
	\include{chapters/chapter04}\cleardoublepage

\ctparttext{
\todo{ Update intro to methods part}
You can put some informational part preamble text here. 
Illo principalmente su nos. Non message \emph{occidental} angloromanic
da. Debitas effortio simplificate sia se, auxiliar summarios da que,
se avantiate publicationes via. Pan in terra summarios, capital
interlingua se que. Al via multo esser specimen, campo responder que
da. Le usate medical addresses pro, europa origine sanctificate nos se.}
\part{Proposed Cost-Sensitive Methods}\label{part:2}

  \include{chapters/chapter05}\cleardoublepage
  \include{chapters/chapter06}\cleardoublepage
  \include{chapters/chapter07}\cleardoublepage
  \include{chapters/chapter08}\cleardoublepage
  \include{chapters/chapter09}\cleardoublepage

\addtocontents{toc}{\protect\vspace*{\baselineskip}\protect}
\cleardoublepage
\makeatletter
\def\toclevel@chapter{-1}
\makeatother
    
\include{chapters/chapter10}


% % Back pages ==================================================================
\appendix
\cleardoublepage
\part{Appendix}

\cleardoublepage\include{frontback/notations}
\cleardoublepage\include{frontback/bibliography}
		

\end{document}
