%*******************************************************
% Publications
%*******************************************************
\pdfbookmark[1]{Publications}{publications}
\chapter*{Publications}
This dissertation summarizes several contributions to the field of example-dependent 
cost-sensitive machine learnings. Publications that have directly stemmed from this work 
include:
\bigskip

\begin{itemize}
\item \citep{CorreaBahnsen2013} \textit{Cost Sensitive Credit Card Fraud Detection Using Bayes 
Minimum Risk},
Alejandro Correa Bahnsen,  Aleksandar Stojanovic, Djamila Aouada and Bj\"rn Ottersten.
In ICMLA: International Conference on Machine Learning and Applications, 2013.

\item \citep{CorreaBahnsen2014} \textit{Improving Credit Card Fraud Detection with Calibrated 
Probabilities},
Alejandro Correa Bahnsen, Djamila Aouada and Bj\"rn Ottersten.
In SIAM-ICDM: SIAM International Conference on Data Mining, 2014.

\item \citep{CorreaBahnsen2014b} \textit{Example-Dependent Cost-Sensitive Logistic Regression for 
Credit Scoring},
Alejandro Correa Bahnsen, Djamila Aouada and Bj\"rn Ottersten.
In ICMLA: International Conference on Machine Learning and Applications, 2014.

\item \citep{CorreaBahnsen2015} \textit{Example-Dependent Cost-Sensitive Decision Trees},
Alejandro Correa Bahnsen, Djamila Aouada and Bj\"rn Ottersten.
In Expert Systems with Applications, 2015.

\item \citep{CorreaBahnsen2015a} \textit{A novel cost-sensitive framework for customer churn 
predictive modeling},
Alejandro Correa Bahnsen, Djamila Aouada and Bj\"rn Ottersten.
In Decision Analytics, 2015.

\item \citep{CorreaBahnsen2015b} \textit{Ensembles of Example-Dependent Cost-Sensitive Decision 
Trees},
Alejandro Correa Bahnsen, Djamila Aouada and Bj\"rn Ottersten.
In IEEE Transactions on Knowledge and Data Engineering, 2015.

\item \citep{CorreaBahnsen2015c} \textit{Paper Fraud},
Alejandro Correa Bahnsen, Djamila Aouada and Bj\"rn Ottersten.
In ECML PKDD, 2015.

\end{itemize}